\chapter{Wafer}
\hypertarget{md_external_2data_2UCRArchive__2018_2Wafer_2README}{}\label{md_external_2data_2UCRArchive__2018_2Wafer_2README}\index{Wafer@{Wafer}}
\label{md_external_2data_2UCRArchive__2018_2Wafer_2README_autotoc_md229}%
\Hypertarget{md_external_2data_2UCRArchive__2018_2Wafer_2README_autotoc_md229}%
 This data set was formatted by Robert Olszewski as part of his doctoral thesis (see \mbox{[}1\mbox{]}). Wafer data relate to semi-\/conductor microelectronics fabrication. A collection of inline process control measurements recorded from various sensors during the processing of silicon wafers for semiconductor fabrication constitute the wafer database; each dataset in the wafer database contains the measurements recorded by one sensor during the processing of one wafer by one tool. The two classes are normal and abnormal process. There is a large class imbalance (10.\+7\% of the train and 12.\+1\% of the test are abnormal).

Train size\+: 1000

Test size\+: 6164

Missing value\+: No

Number of classses\+: 2

Time series length\+: 152

Data donated by Robert Olszewski (see \mbox{[}1\mbox{]}, \mbox{[}2\mbox{]}).

\mbox{[}1\mbox{]} Olszewski, Robert T. Generalized feature extraction for structural pattern recognition in time-\/series data. No. CMU-\/\+CS-\/01-\/108. Carnegie Mellon University, School of Computer Science, 2001. URL \href{https://dl.acm.org/citation.cfm?id=935627}{\texttt{ https\+://dl.\+acm.\+org/citation.\+cfm?id=935627}}

\mbox{[}2\mbox{]} \href{http://www.timeseriesclassification.com/description.php?Dataset=Wafer}{\texttt{ http\+://www.\+timeseriesclassification.\+com/description.\+php?\+Dataset=\+Wafer}} 