\chapter{ECG5000}
\hypertarget{md_external_2data_2UCRArchive__2018_2ECG5000_2README}{}\label{md_external_2data_2UCRArchive__2018_2ECG5000_2README}\index{ECG5000@{ECG5000}}
\label{md_external_2data_2UCRArchive__2018_2ECG5000_2README_autotoc_md59}%
\Hypertarget{md_external_2data_2UCRArchive__2018_2ECG5000_2README_autotoc_md59}%
 The original data set for {\itshape ECG5000} is a 20-\/hour long ECG downloaded from Physionet\+\_\+\+ATM \mbox{[}1\mbox{]}. The database is BIDMC Congestive Heart Failure Database(chfdb) and the record is chf07. It was originally published by Goldberger et al. \mbox{[}2\mbox{]}. The data were pre-\/processed in two steps, first extracting each heartbeat and then making each heartbeat equal length using interpolation. These data were originally used by Chen et al. \mbox{[}3\mbox{]}. After that, 5000 heartbeats were randomly selected to make the current data set. Data were from a patient who has severe congestive heart failure. The class values were obtained by automated annotation.

Train size\+: 500

Test size\+: 4500

Missing value\+: No

Number of classses\+: 5

Time series length\+: 140

Data donated by Yanping Chen and Eamonn Keogh (see \mbox{[}3\mbox{]}, \mbox{[}4\mbox{]}).

\mbox{[}1\mbox{]} \href{https://physionet.org/cgi-bin/atm/ATM}{\texttt{ https\+://physionet.\+org/cgi-\/bin/atm/\+ATM}}

\mbox{[}2\mbox{]} Goldberger, Ary L., et al. "{}\+Physio\+Bank, Physio\+Toolkit, and Physio\+Net\+: components of a new research resource for complex physiologic signals."{} Circulation 101.\+23 (2000)\+: e215-\/e220.

\mbox{[}3\mbox{]} Chen, Yanping, et al. "{}\+A general framework for never-\/ending learning from time series streams."{} Data Mining and Knowledge Discovery 29.\+6 (2015)\+: 1622-\/1664.

\mbox{[}4\mbox{]} \href{http://www.timeseriesclassification.com/description.php?Dataset=ECG5000}{\texttt{ http\+://www.\+timeseriesclassification.\+com/description.\+php?\+Dataset=\+ECG5000}} 