\chapter{Trace}
\hypertarget{md_external_2data_2UCRArchive__2018_2Trace_2README}{}\label{md_external_2data_2UCRArchive__2018_2Trace_2README}\index{Trace@{Trace}}
\label{md_external_2data_2UCRArchive__2018_2Trace_2README_autotoc_md221}%
\Hypertarget{md_external_2data_2UCRArchive__2018_2Trace_2README_autotoc_md221}%
 This data set is a subset of the Transient Classification Benchmark (Trace project), an initiative at the turn of the twentieth century to collate data from the application domain of the process industry (e.\+g. nuclear, chemical, etc.). It is a synthetic data set designed to simulate instrumentation failures in a nuclear power plant, created by Davide Roverso (see \mbox{[}1\mbox{]}). The full data set consists of 16 classes, with 50 instances in each class. Each instance has four features.

The {\itshape Trace} subset is a four-\/class time series classification problem. It only uses the second feature of class 2 and 6, and the third feature of class 3 and 7. All instances are linearly interpolated to have the same length of 275 data points, and are z-\/normalized. The data were used in \mbox{[}2\mbox{]}.

Train size\+: 100

Test size\+: 100

Missing value\+: No

Number of classses\+: 4

Time series length\+: 275

Data donated by Davide Roverso (see \mbox{[}1\mbox{]}, \mbox{[}2\mbox{]}, \mbox{[}3\mbox{]}).

\mbox{[}1\mbox{]} Roverso, Davide. "{}\+Multivariate temporal classification by windowed wavelet decomposition and recurrent neural networks."{} 3rd ANS international topical meeting on nuclear plant instrumentation, control and human-\/machine interface. Vol. 20. 2000.

\mbox{[}2\mbox{]} Ratanamahatana, Chotirat Ann, and Eamonn Keogh. "{}\+Making time-\/series classification more accurate using learned constraints."{} Proceedings of the 2004 SIAM International Conference on Data Mining. Society for Industrial and Applied Mathematics, 2004.

\mbox{[}3\mbox{]} \href{http://www.timeseriesclassification.com/description.php?Dataset=Trace}{\texttt{ http\+://www.\+timeseriesclassification.\+com/description.\+php?\+Dataset=\+Trace}} 